Collision rates of planetesimals near mean-motion resonances

### 2020-12-11 refereeResponse.txt

    As shown in figure 6 (fig 5 in the original version), the bump and dip features at the center of the MMRs are still present, even if we ignore particles whose semimajor axis falls within the libration width of the resonances. What this implies is that the edges of the resonances are important. As we approach a resonance from the outside, the critical angle \phi approaches an unstable equilibirum where it is stationary. Where the critical angle is near-stationary, the pericenter orientations of the planetesimals experience a torque which causes their \varpi to follow the giant planet in its orbit. This is what we propose is responsible for the coherent structure seen in the right-hand panels of figures 7 and 8 (6 and 7 in the original paper), along with the structure seen in the collision profiles.

@@

    The paragraph referenced now clarifies that we are specifically referring to collisions between bodies inside of the libration width of the resonance. An additional sentence has been added at the end of the following paragraph (which provides an explanation for the nonaxisymmetric gaps seen in fig 1) to tie this back to figure 6.

37) pg.6 rcol P.2 l.38-56 - "As mentioned in section 2, ... appears to 'follow' the planet." - This paragraph is super confuse. I don't understand this. Why not simply say this is caused by the secular forcing in eccentricity? This would save 3 paragraphs in the paper and would be much more clear.

    See 36). If you look at figures 1, 7 and 8, (1, 6 and 7 in the original paper) the nonaxisymmetric gap structure in the disk near the resonances is always aligned with the planet's orbital phase. It is also apparent from figure 1 that the gaps are not aligned with the planet's longitude of pericenter, which should be the case if the structure were due to secular forcing in eccentricity. Furthermore, orbits of bodies in resonance experience significant precession, which randomizes their orientations. The gap structure cannot be due to the interface between the secularly forced, non-resonant part of the disk, and the randomly oriented orbits of bodies in resonance. The latter explanation was given by Tabeshian & Weigert 2016, which, as we point out in our paper, does not quite make sense.

@@

40) pg.10 lcol P.4 l.42-44 - "Many different parameterizations are possible, depending on optical depth, grain size, disc temperature, etc.,..." - But couldn't this change all of your conclusions? Please, see my concerns regarding planetesimal sizes and add discussion.

    Ask Aaron about this?

41) Last paragraph of section 5 - "In order to... cases shown above" - This is a big IF, especially if what the authors are measuring here is the planetesimal collisional profile rather than the dust profile, or if the dust profile would be even shallower as a consequence of aerodynamic drag acting on small fragments of collisionally evolved planetesimals.

    This is certainly a big if, although we have shown with a back-of-the-envelope calculation in section 4.2 that it could be plausible. We have added some additional text to the end of section 5 to remind the reader that the dust profile is built on some not-so-solid assumptions.

@@

44) pg.12 rcol P.4 l.50-52 - "As we have shown, the bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs." - Please, see my concern and add discussion.

    This is addressed in a few other places in the new version of the paper, but we have added a sentence here reminding the reader of the assumption that goes into constucting the dust profile.

My apologies for being so long. I do think this work has potential, but it does need substantial clarifications.

	No need to apologize. We appreciate your thoroughness and care!
